Scheduling and Vectorization for MPC

### 2022-03-05 paper_SIMD.tex
Minor edit.

\item We present a compiler that takes a Python-like high-level 
program and produces amortized (i.e., vectorized) low-level cryptographic 
code in the MOTION framework. Central to our approach is a new 
vectorization algorithm that produces optimal schedules for a large 
number of MPC programs.

>>>>

\item We present a compiler that takes an IMP-like high-level 
program and produces amortized (i.e., vectorized) low-level cryptographic 
code in the MOTION framework. Central contributions are 1) a novel compiler framework, 
2) a vectorization algorithm that produces optimal schedules for a large 
number of MPC programs, and 3) reasoning over output arrays without Array SSA; we remove 
infeasible loop-carried dependences introduced by standard SSA to improve vectorization.
